ML-based approach for accelerating global search algorithm for solving multicriteria problems\thanks{Supported by organization x.}

### 2022-02-07 2022/LION/main.tex
lambda

Any effective (Pareto-optimal) variant  in which it is impossible to reduce the values of all criteria $f_i (y)$, $1 \leq i \leq s$, at once by choosing another option   can be considered as a partial solution to the MCO problem. In practice, various scalarization techniques are often used to find effective solutions \cite{Ehrgott2005,Pardalos2017,Marler2004,GergelKozinov2020}. The present study uses the minimax convolution of partial criteria that possesses good theoretical properties
\begin{equation}
\min{f(y)} \to \min_{y\in D}{\max_{1 \leq i \leq s}{(f_i (y) \lambda_i )}} ,
\label{eq:4}
\end{equation}
where $\lambda_i \geq 0$, $1 \leq i \leq s$, are numerical indicators of the significance of each criterion.

In general case, the entire set of Pareto-optimal variants is taken as a complete solution to the MCO problem. For the numerical building of an approximation of the Pareto set a number of scalar optimization problems (\ref{eq:4}) are solved with different coefficients $\lambda_i \geq 0$, $1 \leq i \leq s$.

>>>>

Any effective (Pareto-optimal) variant  in which it is impossible to reduce the values of all criteria $f_i (y)$, $1 \leq i \leq s$, at once by choosing another option   can be considered as a partial solution to the MCO problem. In practice, various scalarization techniques are often used to find effective solutions \cite{Ehrgott2005,Pardalos2017,Marler2004,GergelKozinov2020}. The present study uses the minimax convolution of partial criteria that possesses good theoretical properties
\begin{equation}
\min{f(y)} \to \min_{y\in D}{\max_{1 \leq i \leq s}{(f_i (y) \lambda_i )}} ,
\label{eq:4}
\end{equation}
where $\lambda_i \geq 0$, $1 \leq i \leq s$, $\sum_{i=1}^s{\lambda_i}=1$, are numerical indicators of the significance of each criterion.

In general case, the entire set of Pareto-optimal variants is taken as a complete solution to the MCO problem. For the numerical building of an approximation of the Pareto set a number of scalar optimization problems (\ref{eq:4}) are solved with different coefficients $\lambda_i \geq 0$, $1 \leq i \leq s$, uniformly distributed
%in the space of ones.
\textcolor[rgb]{1,0,0}{in $[0,1]$.}
